---
title: "vignette"
author: "Saskia Freytag, Montana Spiteri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

nicheR is a user-friendly R package providing functions to identify spatial niches from spatial transcriptomics data. 

All functions in this package are compatible with the `r BiocStyle::Biocpkg("SpatialExperiment")` infrastructure and may be utilised with polygon and/or dots from spatial data. 

The package can provide information of the unique niches present in spatial data and also holds capabilities to map cells back to niches for optimal inference of cellular neighbourhoods. 

# Installation

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("MontanaSpiteri/nicheR")
```

# Quick Start

```{r setup}
library(nicheR)
```

# Load Dataset

```{r}

```

